nextflu: Real-time tracking of seasonal influenza H3N2 virus evolution in humans

### 2015-04-01 manuscript/nextflu.tex
Switch to one line per sentence.
I'm sorry if this makes you crazy, but one-line-per-sentence really
helps reduce merge conflicts when collaborating via TeX.

The frequency plot below the tree (see \FIG{freq}) displays the frequency trajectory
of clades in the tree whenever the mouse hovers above the branch defining the clade. 
Furthermore, trajectories of individual mutations, combinations of two mutations, and 
predifined clades such as 3c3.a can be plotted by entering them in text field
\begin{figure}[bhtp]
	\begin{center}
	\includegraphics[width=0.99\columnwidth]{figures/frequencies}
\caption[]{The frequency diagram on \url{nextflu.org} allows geography specific
		plotting of frequencies of individual mutations, pairs of mutations, 
		predefined genotypes, as well as clades in the tree. }
\label{fig:freq}
\end{center}
\end{figure}

>>>>

The frequency plot below the tree (see \FIG{freq}) displays the frequency trajectory of clades in the tree whenever the mouse hovers above the branch defining the clade. 
Furthermore, trajectories of individual mutations, combinations of two mutations, and predifined clades such as 3c3.a can be plotted by entering them in text field.

\begin{figure}[bhtp]
	\begin{center}
	\includegraphics[width=0.99\columnwidth]{figures/frequencies}
\caption[]{The frequency diagram on \url{nextflu.org} allows geography specific
		plotting of frequencies of individual mutations, pairs of mutations, 
		predefined genotypes, as well as clades in the tree. }
\label{fig:freq}
\end{center}
\end{figure}
